\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-01 paper.tex
ralph's comments

\begin{abstract}
	% abstract goes here
	\begin{figure}[h]
		\centering
		\includegraphics[width=\textwidth]{abstract.jpg}
		% Note: you don't actually need the part in square brackets for the
		% caption, but if you omit it the regular caption text will be used for
		% the List of Figures entry.
		\caption[\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock]
		{\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock, National
			Gallery of Art, Washington, D.C.}
		\label{fig:abstract}
	\end{figure}
\end{abstract}

@@

We would like to thank Atticus Sims, CEO and founder of Kyoto~VR, for sponsoring
this project and providing help and guidance throughout our time in Japan. His
knowledge of the history of Kinkaku-ji and Kyoto in general has been invaluable
to our experience.

We would also like to thank Inoue Hikaru for his help with translations and
researching AR technology. A special thank you to the IQP team working with
Kyoto~VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
filming and editing the app trailer, as well as providing help with testing.

Finally, a thank you to our advisers, Professors Joshua Cuneo and Ralph Sutter.
Without their expert advice and feedback this project probably could not have
been completed.

@@

Our team built, tested and polished a mobile app to deliver an audio tour,
incorporating various augmented reality (AR) features to enhance the
experience. Our app delivers a tour of Kinkaku-ji, or The Temple of the Golden
Pavilion, a popular tourist destination in Kyoto. In this app, which we call
ARuko, many of the AR features were aimed at improving accessibility. These
features include translating signs and providing additional info on the
physical map located at the site. Other features were purely for spectacle,
such as the ability to take an AR ``souvenir'' home by scanning the ticket
to enter Kinkaku-ji.

ARuko went through multiple iterations of user testing and bug testing at
Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
\ref{sec:finalFieldTesting} go into detail about our two days of field testing
on-site. From these tests, we were able to refine the user experience, and
identify important features to add to the app. Much of the app's functionality
was dictated by Atticus Sims, C.E.O and founder of Kyoto~VR, who plans to
monetize the app. We also worked with an IQP team, who had been tasked with
exploring funding options and creating promotional content.

@@

The field of consumer-oriented augmented reality (AR) technology is just coming
into full swing, and it presents many unique opportunities for a myriad of
fields. This budding technological platform uses digital displays to augment
real-world information with computer-generated data. As the technology
progresses, several disparate industries have found novel uses for it, some
becoming extremely profitable~\autocite{webster2018}. With smartphone
manufacturers investing billions into AR technology~\autocite{mason2016}, it
seems poised to be the next big digital interface.

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. This technology can provide
accessible information to tourists and art viewers that they would not be able
to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto, is the
perfect example of a site that would benefit from AR~\autocite{bornoff2000}.
Kinkaku-ji is a UNESCO World Heritage Site~\autocite{unesco} and one of the
most popular tourist destinations in Japan~\autocite{japanguide2019}. The
Golden Pavilion is a magnificent sight to behold, but the gardens and grounds
are the true beauty of Kinkaku-ji. It is a living masterpiece of Zen Buddhist
landscape design, expanding on the natural beauty of Kyoto's forests and
mountains through the practice of borrowed scenery~\autocite{kuitert2002}.

However, much of the historic information at the site is lost on visitors
because it is not readily available to non-Japanese speakers. What few signs and
displays exist are presented only in Japanese, and do not provide most of the
history and context necessary to fully understand Kinkaku-ji.

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. The experience of walking through the site is enhanced by
informative narration and AR pop-ups that do not alter the buildings or ground
in real life.

@@

As smartphones and mobile technology become more prevalent, new forms of
human-computer interaction are becoming mainstream. Smartphones allow for an
unprecedented degree of connectivity with the digital world, but can also serve
as a tool for enhancing the physical world. In this section we explain the
origins and uses of some of this technology.

@@

Augmented reality, or AR, is a type of human-computer interface where
perceptions of the real world are enhanced by computer-generated information.
This differs from virtual reality (VR) in that a VR experience consists
exclusively of virtual information. In AR, virtual information is mixed with
sensory input from the real world~\autocite{carmigniani2011}. This can enhance
the user's perception of reality by providing information that would be
difficult or impossible to display through traditional means.

For example, AR can be used to display information about historical events,
places, and objects overlaid onto images of the real
world~\autocite{saenz2009}.  This provides the user with useful information
without needing to alter a real historic site.

@@

Many of the existing applications using AR, in our eyes, do not leverage the
full potential of this emerging technology. As with any new field, our
understanding of AR and how to develop for it is limited. All sorts of
different challenges and limitations face the development and production of AR
apps. Here are some that we considered when working on our app.

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. Many AR apps and features available on smartphones offer
very little in the way of functionality or practicality; quite simply, they are
primarily used for minor spectacles and simple
tricks~\autocite{theappsolutions2018}. For example, one of the most popular
apps to use AR, \textit{Pokémon Go}, primarily uses its AR feature to place a
Pokémon on top of a camera's video feed. Disappointingly, it does not interact
with anything around it. It just floats a fixed distance away from the user.

@@

Viro AR comes in two flavors: ViroReact and ViroCore\autocite{facebook2019}.
ViroCore allows developers to build an AR Application with Java. The
disadvantage of this is that ViroCore only allows developers to target Android,
which unfortunately made ViroCore not an option for our project. ViroReact is
the cross-platform option for ViroAR. ViroReact leverages the cross-platform
capabilities of React, which is Facebook's JavaScript Library for developing
user interfaces~\autocite{facebook2019}.

@@

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way
to successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The takeaway is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone hardware to the limit, emulation is not something
is not something we wanted to struggle with. On top of this, our testing
required us to move the camera through the world at various speeds and angles,
which is simply cumbersome with a laptop webcam.

@@

Unity is a game engine that was originally introduced in
2005~\autocite{axon2016}. Because of the low barrier to entry---knowledge-wise
and price-wise---the engine quickly became incredibly popular. Ironically,
because the engine is so accessible that, Unity has faced a degree of critism.
Because Unity appeals to so many beginners, there are many unpolished games that
bear the Unity logo. In response to this sentiment, Marcos Sanchez, head of
global communications at Unity, "Democratizing development---in our minds, we
don’t think is the wrong thing, we think it’s the right thing. You want more
people understanding, and everyone’s gotta start somewhere." Unity CEO John
Riccitiello made the claim at TechCrunch Disrupt San Francisco that half of all
games are made with Unity \autocite{dillet2018}. We consider Unity's ubiquity to
be an advantage; there is a glut of information about how to use augmented
reality within Unity.
%TODO citing a quotation from inside the first citation. Is this okay?

@@

None of this history is readily apparent to a casual tourist at Kinkaku-ji.
There are a few signs describing different areas, but they are only available in
Japanese and contain very little information about the history and design of the
site. Because of this, an intuitive audio tour app with AR features would be
very helpful to tourists at Kinkaku-ji.

@@

For testing and development purposes the Editour backend was originally hosted
on a personal server belonging to a member of our team. This was a CentOS
virtual machine running on an old Dell rack server in Worcester, Massachusetts.
We wrote a custom systemd service to run the Editour as a daemon and keep its
log files organized. The Node.js backend was served by an Nginx reverse proxy
running on the same virtual machine.

@@

Despite Kinkaku-ji being an incredibly popular tourist destination that draws
crowds from all over the world, the majority of the signage is purely Japanese.
While AR translation apps exist, the experience can be frustrating, and produce
poor results. Google's text recognition and machine-learning powered translation
technology is certainly impressive. At the same time, the translation service
works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
the app attempts to translate text as quickly as possible, superimposing the
translated text onto the real world using the camera. In ``scan'' mode, the user
first takes a photo. Then, the user is prompted to highlight where text appears
in the photo. After the translation is complete, the translated text appears in
a separate UI element instead superimposed onto the photo. In most cases, it is
more convenient and readable to have the translation appear in a separate
scrollable textbox. This motivated the current design of the ``info buttons'' in
ARuko. Instead of placing text directly onto signage, we place a blue button
with a stylized `i' in the center. By tapping on this button, a separate UI
element will appear containing the translated text. Since this button is cast
into the world using the AR camera, the button appears to be placed directly
onto the content in the real world.

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{kinkakuji-ticket.jpeg}
    \caption{Map overlay displaying the path and translated labels}
    \label{fig:kinkakujiTicket}
\end{figure}

@@

We found a free untextured model of the Golden Pavilion to use for this
feature. Using Unity's built-in capability to design materials, we created
a shiny golden material and applied it to the model.

>>>>

\begin{abstract}
	% abstract goes here
	% TODO write abstract
\end{abstract}

@@

Our team would like to thank Atticus Sims, CEO and founder of Kyoto~VR, for
sponsoring this project and providing help and guidance throughout our time in
Japan. His knowledge of the history of Kinkaku-ji and Kyoto in general has been
invaluable to our experience.

We would also like to thank Inoue Hikaru for his help with translations and
researching AR technology. A special thank you to the IQP team working with
Kyoto~VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
filming and editing the app trailer, as well as providing help with testing.
Further, we are grateful to the assistance and resources provided by Ritsumeikan
University and Professor Noma Haruo. Finally, a thank you to our advisers,
Professors Joshua Cuneo and Ralph Sutter. Without their expert advice and
feedback this project probably could not have been completed.

@@

Our team consists of three Senior Worcester Polytechnic Institute (WPI)
students: William Campbell, computer science and interactive media and game
development double major; Cole Granof, computer science major; and Joseph
Petitti, computer science major. We spent twelve weeks in Shiga, Japan
completing the requirements for our Major Qualifying Project, a WPI graduation
requirement in which students solve a real-world problem through practical
project-based work. Our project was sponsored by Kyoto~VR, a startup founded in
2016 to ``document and preserve the culture and heritage of the city and
communicate the richness of Japan’s Old Capital to the
world''~\autocite{kyotovr2018}.

Our team worked directly under Kyoto VR founder and CEO Atticus Sims to develop
and tested a mobile app to deliver an audio tour, incorporating various
augmented reality (AR) features to enhance the experience. Our app delivers a
tour of Kinkaku-ji, or The Temple of the Golden Pavilion, a popular tourist
destination in Kyoto. In this app, which we call ARuko, many of the AR features
were aimed at improving accessibility. These features include translating signs
and providing additional info on the physical map located at the site. Other
features were purely for spectacle, such as the ability to take an AR
``souvenir'' home by scanning the ticket to enter Kinkaku-ji.

ARuko went through multiple iterations of user testing and bug testing at
Kinkaku-ji. Sections~\ref{sec:initialFieldTesting} and
\ref{sec:finalFieldTesting} go into detail about our two days of field testing
on-site. From these tests, we were able to refine the user experience, and
identify important features to add to the app. Much of the app's functionality
was decided by our project sponsor, who plans to monetize the app. We also
worked with an IQP team, who had been tasked with exploring funding options and
creating promotional content.

@@

The field of consumer-oriented augmented reality (AR) technology is just coming
into full swing, and it presents many unique opportunities for a myriad of
fields. This budding technological platform uses digital displays to augment
real-world information with computer-generated data (see
Figure~\ref{fig:arExample}. As the technology progresses, several disparate
industries have found novel uses for it, some becoming extremely
profitable~\autocite{webster2018}. With smartphone manufacturers investing
billions into AR technology~\autocite{mason2016}, it seems poised to be the next
big digital interface.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{ar-example.jpg}
	% Note: you don't actually need the part in square brackets for the
	% caption, but if you omit it the regular caption text will be used for
	% the List of Figures entry.
	\caption[A virtual model of the solar system projected onto the real world
	using AR]{A virtual model of the solar system projected onto the real world
		using augmented reality~\autocite{tedx2016}}
	\label{fig:arExample}
\end{figure}

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. This technology can provide
accessible information to tourists and art viewers that they would not be able
to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto (see
Figure~\ref{fig:kinkakuji1}, is the perfect example of a site that would benefit
from AR~\autocite{bornoff2000}.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-1.jpg}
	\caption[The Golden Pavilion]{The Golden Pavilion~\autocite{fan2018}}
	\label{fig:kinkakuji1}
\end{figure}

Kinkaku-ji is a UNESCO World Heritage Site~\autocite{unesco} and one of the
most popular tourist destinations in Japan~\autocite{japanguide2019}. The
Golden Pavilion is a magnificent sight to behold, but the gardens and grounds
are the true beauty of Kinkaku-ji. It is a living masterpiece of Zen Buddhist
landscape design, expanding on the natural beauty of Kyoto's forests and
mountains through the practice of borrowed scenery~\autocite{kuitert2002}.

However, much of the historic information at the site is lost on non-Japanese
speaking visitors because it is often only available in Japanese. In addition to
the language barrier, the information provided does not include most of the
history and context necessary to fully understand Kinkaku-ji.

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. Many AR apps require specific markers, like the those shown in
Figure~\ref{fig:arMarker}. Too avoid needing to place any physical object that
would disturb the buildings or grounds of a historic site our app does not rely
on these markers. Instead, our ARuko recognizes images of objects that are
already at the site, and uses them to display informative AR pop-ups. See
Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for
more details.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{ar-marker.jpg}
	\caption[Augmented reality markers]{Augmented reality
		markers~\autocite{jeriaska2010}}
	\label{fig:arMarker}
\end{figure}

@@

As smartphones and mobile technology become more prevalent, new forms of
human-computer interaction are becoming mainstream. Smartphones allow for an
unprecedented degree of connectivity with the digital world, but can also serve
as a tool for digitally enhancing the physical world. In this section we explain
the origins and uses of some of this technology.

@@

Augmented reality, or AR, is a type of human-computer interface where
perceptions of the real world are enhanced by computer-generated information.
This differs from virtual reality (VR) in that a VR experience consists
exclusively of virtual information in a virtual environment. In AR, virtual
information is mixed with sensory input from the real
world~\autocite{carmigniani2011}. This can enhance the user's perception of
reality by providing information that would be difficult or impossible to
display through traditional means.

For example, AR can be used to display information about historical events,
places, and objects overlaid onto images of the real
world~\autocite{saenz2009}, in a way that is more intuitive or visually
appealing than a purely virtual environment. This provides the user with useful
information without needing to alter a real historic site.

@@

Most existing applications using AR, in our team's opinions, do not leverage the
full potential of this emerging technology. As with any new field, our
understanding of AR and how to develop for it is limited. All sorts of different
challenges and limitations face the development and production of AR apps. Here
are some that we considered when working on our app.

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. Many AR apps and features available on smartphones offer
very little in the way of functionality or practicality; quite simply, they
primarily primarily revolve around deploying
gimmicks~\autocite{theappsolutions2018}. For example, one of the most popular
apps to use AR, \textit{Pokémon Go}, primarily uses its AR feature to place a
Pokémon on top of a camera's video feed. Disappointingly, it does not interact
with anything around it. It just floats a fixed distance away from the user.

@@

Viro AR comes in two versions: ViroReact and ViroCore\autocite{facebook2019}.
ViroCore allows developers to build an AR Application with Java. The
disadvantage of this is that ViroCore only allows developers to target Android,
which unfortunately made ViroCore not an option for our project. ViroReact is
the cross-platform option for ViroAR. ViroReact leverages the cross-platform
capabilities of React, which is Facebook's JavaScript Library for developing
user interfaces~\autocite{facebook2019}.

@@

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way
to successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The takeaway is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone hardware to the limit, emulation is not something we
wanted to struggle with. On top of this, our testing required us to move the
camera through the world at various speeds and angles, which is simply
cumbersome with a laptop webcam.

@@

Unity is a game engine that was originally introduced in
2005~\autocite{axon2016}. Because of the low barrier to entry---knowledge-wise
and price-wise---the engine quickly became incredibly popular. Ironically,
because the engine is so accessible that, Unity has faced a degree of critism.
Because Unity appeals to so many beginners, there are many unpolished games that
bear the Unity logo. In response to this sentiment, Marcos Sanchez, head of
global communications at Unity, "Democratizing development---in our minds, we
don't think is the wrong thing, we think it's the right thing. You want more
people understanding, and everyone’s gotta start somewhere"~\autocite{axon2016}.
Unity CEO John Riccitiello made the claim at TechCrunch Disrupt San Francisco
that half of all games are made with Unity \autocite{dillet2018}. We consider
Unity's ubiquity to be an advantage; there is a glut of information about how to
use augmented reality within Unity.

@@

None of this history is readily apparent to a typical non-Japanese speaking
tourist at Kinkaku-ji. There are a few signs describing different areas, but
they are only available in Japanese and contain very little information about
the history and design of the site. Because of this, an intuitive audio tour app
with AR features would be very helpful to tourists at Kinkaku-ji.

@@

For testing and development purposes the Editour backend was originally hosted
on Joseph Petitti's personal server. This was a CentOS virtual machine running
on an old Dell rack server in Worcester, Massachusetts. We wrote a custom
systemd service to run the Editour as a daemon and keep its log files organized.
The Node.js backend was served by an Nginx reverse proxy running on the same
virtual machine.

@@

ARuko uses augmented reality to translate text at the site as well. While AR
translation apps exist, the experience can be frustrating, and produce poor
results. Google's text recognition and machine-learning powered translation
technology is certainly impressive. At the same time, the translation service
works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
the app attempts to translate text as quickly as possible, superimposing the
translated text onto the real world using the camera. In ``scan'' mode, the user
first takes a photo. Then, the user is prompted to highlight where text appears
in the photo. After the translation is complete, the translated text appears in
a separate UI element instead superimposed onto the photo. In most cases, it is
more convenient and readable to have the translation appear in a separate
scrollable text box. This motivated the current design of the ``info buttons''
in ARuko. Instead of placing text directly onto signage, we place a blue button
with a stylized `i' in the center. By tapping on this button, a separate UI
element will appear containing the translated text. Since this button is cast
into the world using the AR camera, the button appears to be placed directly
onto the content in the real world.

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{kinkakuji-ticket.jpeg}
    \caption{Kinkaku-ji ticket}
    \label{fig:kinkakujiTicket}
\end{figure}

@@

We found a free untextured model of the Golden Pavilion to use for this
feature. Using Unity's built-in capability to design materials, we created
a shiny golden material and applied it to the model (see
Figure~\ref{fig:souvenir}.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{souvenir.png}
	\caption{ARuko's virtual souvenir feature}
	\label{fig:souvenir}
\end{figure}
